Exploring the Role of Feedback in Machine Learning Jupyter Notebooks

### 2024-05-14 report/emse24.tex
feat(report): emse24 updates

\subsubsection{Network architecture check ($N = 1$)}
% (A11)

When integrating pre-trained models or leveraging transfer learning techniques, it is crucial to ensure the compatibility of the custom neural network architecture with the pre-trained components. This is particularly important when combining convolutional layers from different sources, as the spatial dimensions and channel configurations must align correctly.

@@

\subsubsection{Value check (A30, A41, A44--46, A52, A65, A68, A69, A73, A92)}

Check that the values in a column are in the specified values (categorical) or in a specified range (normalised continuous variable) or binary (such as the label column).

% NOTE: blanks and unit-tests
\subsubsection{Miscellaneous checks (A6, A20, A32, A34, A36, A53, A62, A75, A83, A87, A97)}

These feel like unit tests, performed in lieu of writing full test suites in the notebook.

%\begin{acknowledgements}
%If you'd like to thank anyone, place your comments here
%and remove the percent signs.
%\end{acknowledgements}

% Authors must disclose all relationships or interests that 
% could have direct or potential influence or impart bias on 
% the work: 
%
% \section*{Conflict of interest}
%
% The authors declare that they have no conflict of interest.

>>>>

\subsubsection{Network architecture check ($N = 3$)}
% (A11, A62, A75)

% TODO: revisit this section; we have new assertions
When integrating pre-trained models or leveraging transfer learning techniques, it is crucial to ensure the compatibility of the custom neural network architecture with the pre-trained components. This is particularly important when combining convolutional layers from different sources, as the spatial dimensions and channel configurations must align correctly.

@@

\subsubsection{Data validation check ($N = 11$)}
% formerly value-check (A20, A30, A41, A44--46, A52, A65, A68, A69, A73, A83, A92)

% TODO: revisit, we have new assertions here; update the count
we encountered a range of assert statements that perform various validation checks on data structures, such as NumPy arrays and pandas DataFrames. These checks help ensure the data meets specific criteria or constraints, preventing potential errors or inconsistencies in downstream operations.

One type of validation check involves verifying the presence of specific values or ranges within arrays or columns. For example, the assertion \emph{A41}:~\lstinline{assert np.all(np.unique(X['smoke'].values) == np.array([0, 1]))} checks if the unique values in the \texttt{smoke} column of the DataFrame \texttt{X} are limited to 0 and 1. Similarly, \emph{A65}~\lstinline{assert np.all(y <= nb_classes)} ensures that all values in the array \texttt{y} are less than or equal to a certain number of classes.

Another common validation check is verifying the equality or closeness of values or arrays. The assertion \emph{A44}:~\lstinline{assert abs(min(entity_embedding[low:high]) - max(entity_embedding[low:high])) <= 1} checks if the difference between the minimum and maximum values in a specific range of the \texttt{entity\_embedding} array is less than or equal to 1. Similarly, \emph{A46}:~\lstinline{assert np.isclose(stdev_norm, 1.0, atol=1e-16)} verifies that the \texttt{stdev\_norm} value is close to 1.0 within a specified absolute tolerance.

Some assertions focus on validating the uniqueness or cardinality of values in arrays or DataFrames. For instance, \emph{A52}:~\lstinline{assert grouped_users['user_id'].nunique() == user_engagement['user_id'].nunique()} checks if the number of unique user IDs in the \texttt{grouped\_users} DataFrame is equal to the number of unique user IDs in the \texttt{user\_engagement} DataFrame.

Other assertions validate the presence of specific values or conditions within DataFrames or other data structures. The assertion \emph{A73}:~\lstinline{assert df['clf'].value_counts()[1] == len(df[df['quality'] >= 7])} checks if the count of a specific value (1) in the ``clf'' column of the DataFrame \texttt{df} is equal to the number of rows where the ``quality'' column is greater than or equal to 7.

By verifying specific conditions, value ranges, uniqueness, and equality constraints, these assertions help catch potential errors or inconsistencies early in the pipeline, preventing downstream issues and ensuring reliable and accurate results.
